Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-10 slides.Rmd
autogit

---
#title: "Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming"
subtitle: "Kolloquium zur Masterarbeit im M.Sc. Wirtschaftspädagogik "
author: "Roman Hoehn"
institute: "Johannes Gutenberg-Universität Mainz"
date: "Datum: 25.01.2023"
fontsize: 11pt
link-citations: true
output:
  beamer_presentation:
    theme: "Madrid"
    fonttheme: "structurebold"
    fig_width: 12
    fig_height: 10
    # keep_tex: true
    fig_caption: no
    number_sections: true
    slide_level: 2
toc: yes
bibliography: ref/ref.bib
csl: csl/harvard-cite-them-right.csl
includes:
      in_header: [header_files/slides.tex]

@@

knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.pos = "!H")

@@

2 Phase Ansatz:

>>>>

---
title: "Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming"
subtitle: "Kolloquium zur Masterarbeit im M.Sc. Wirtschaftspädagogik "
author: "Roman Hoehn"
institute: "Johannes Gutenberg-Universität Mainz"
date: "Datum: 25.01.2023"
fontsize: 11pt
link-citations: true
output:
  beamer_presentation:
    #theme: "Madrid"
    fonttheme: "structurebold"
    fig_width: 12
    fig_height: 10
    # keep_tex: true
    fig_caption: no
    number_sections: true
    slide_level: 2
toc: yes
bibliography: ref/ref.bib
csl: csl/harvard-cite-them-right.csl
includes:
      in_header: [header_files/slides.tex]

@@

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = "!H")

@@

2 Phasen Ansatz:
